Output Summary

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
ms-content: include a figure showing fit to data

>>>>

```{r obs-vs-fit-fig, fig.width = 7.2, fig.height = 7, eval = params$obs_vs_fit_fig, fig.cap = msdown::prep_caption(obs_vs_fit_fig_caption)}
# initialize an empty list
plot_dat = list()

# prep values to plot: fall trap passage
plot_dat$Pa_fall = list(
  obs = jags_data$Pa_obs[,i_fall,],
  fitted = {
    tmp = post_summ(post, sub_index("^Pa[.+,LH_type,.]", LH_type = i_fall))
    list(
      mn = array_format(tmp["mean",])[,i_fall,],
      lwr = array_format(tmp["2.5%",])[,i_fall,],
      upr = array_format(tmp["97.5%",])[,i_fall,]
    )
  }
)

# prep values to plot: spring trap passage
plot_dat$Mb_spring = list(
  obs = jags_data$Mb_obs[,i_spring,o_nor,],
  fitted = {
    tmp = post_summ(post, sub_index("^Mb[.+,LH_type,origin,.]", LH_type = i_spring, origin = o_nor))
    list(
      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
    )
  }
)

# prep values to plot: adult return to river
plot_dat$Ra_tot = list(
  obs = jags_data$Ra_obs,
  fitted = {
    tmp = post_summ(post, "^Ra_tot[")
    list(
      mn = array_format(tmp["mean",]),
      lwr = array_format(tmp["2.5%",]),
      upr = array_format(tmp["97.5%",])
    )
  }
)

# prep values to plot: summer to LGR survival
plot_dat$phi_Pb_Ma = list(
  obs = plogis(jags_data$Lphi_obs_Pb_Ma),
  fitted = {
    tmp = post_summ(post, "^phi_Pb_Ma[")
    list(
      mn = array_format(tmp["mean",]),
      lwr = array_format(tmp["2.5%",]),
      upr = array_format(tmp["97.5%",])
    )
  }
)

# prep values to plot: fall to LGR survival
plot_dat$phi_Pa_Ma_fall = list(
  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_fall,]),
  fitted = {
    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_fall, pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,i_fall,],
      lwr = array_format(tmp["2.5%",])[,i_fall,],
      upr = array_format(tmp["97.5%",])[,i_fall,]
    )
  }
)

# prep values to plot: winter to LGR survival
plot_dat$phi_Pa_Ma_winter = list(
  obs = plogis(jags_data$Lphi_obs_Pa_Ma[,i_spring,]),
  fitted = {
    tmp = post_summ(post, sub_index("^phi_Pa_Ma[year,LH_type,pop]", year = ".+", LH_type = i_spring, pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,i_spring,],
      lwr = array_format(tmp["2.5%",])[,i_spring,],
      upr = array_format(tmp["97.5%",])[,i_spring,]
    )
  }
)

# prep values to plot: spring to LGR survival (NOR)
plot_dat$phi_Mb_Ma_nor = list(
  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_nor,]),
  fitted = {
    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_nor, pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,i_spring,o_nor,],
      lwr = array_format(tmp["2.5%",])[,i_spring,o_nor,],
      upr = array_format(tmp["97.5%",])[,i_spring,o_nor,]
    )
  }
)

# prep values to plot: spring to LGR survival (HOR)
plot_dat$phi_Mb_Ma_hor = list(
  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,o_hor,]),
  fitted = {
    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,i_spring,o_hor,],
      lwr = array_format(tmp["2.5%",])[,i_spring,o_hor,],
      upr = array_format(tmp["97.5%",])[,i_spring,o_hor,]
    )
  }
)

# prep values to plot: spring to LGR survival (NOR & HOR both)
plot_dat$phi_Mb_Ma = list(
  obs = plogis(jags_data$Lphi_obs_Mb_Ma[,i_spring,,]),
  fitted = {
    tmp = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,.,pop]", year = ".+", LH_type = i_spring, origin = o_hor, pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,i_spring,,],
      lwr = array_format(tmp["2.5%",])[,i_spring,,],
      upr = array_format(tmp["97.5%",])[,i_spring,,]
    )
  }
)

# prep values to plot: LGR to BON (NOR & HOR both)
plot_dat$phi_Ma_O0 = list(
  obs = plogis(jags_data$Lphi_obs_Ma_O0),
  fitted = {
    tmp = post_summ(post, "^phi_Ma_O0[")
    list(
      mn = array_format(tmp["mean",]),
      lwr = array_format(tmp["2.5%",]),
      upr = array_format(tmp["97.5%",])
    )
  }
)

# prep values to plot: BON to LGR (NOR & HOR both)
plot_dat$phi_Rb_Ra = list(
  obs = jags_data$x_LGR/jags_data$x_BON,
  fitted = {
    tmp = post_summ(post, "^phi_Rb_Ra[")
    list(
      mn = array_format(tmp["mean",]),
      lwr = array_format(tmp["2.5%",]),
      upr = array_format(tmp["97.5%",])
    )
  }
)

# add aggregate age/origin compositions
source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-model")
source_rmd_chunk("output-plots-children/03-fit-to-data.Rmd", "calculate-aggregated-comps-data")

# prep values to plot: weir compositon age-3
plot_dat$p_Ra_age3 = list(
  obs = x_Ra_new_obs$x_Ra_age_obs[,k_3,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Ra_age[year,1,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,k_3,],
      lwr = array_format(tmp["2.5%",])[,k_3,],
      upr = array_format(tmp["97.5%",])[,k_3,]
    )
  }
)

# prep values to plot: weir compositon age-4
plot_dat$p_Ra_age4 = list(
  obs = x_Ra_new_obs$x_Ra_age_obs[,k_4,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Ra_age[year,2,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,k_4,],
      lwr = array_format(tmp["2.5%",])[,k_4,],
      upr = array_format(tmp["97.5%",])[,k_4,]
    )
  }
)

# prep values to plot: weir compositon age-5
plot_dat$p_Ra_age5 = list(
  obs = x_Ra_new_obs$x_Ra_age_obs[,k_5,]/apply(x_Ra_new_obs$x_Ra_age_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Ra_age[year,3,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,k_5,],
      lwr = array_format(tmp["2.5%",])[,k_5,],
      upr = array_format(tmp["97.5%",])[,k_5,]
    )
  }
)

# prep values to plot: weir compositon origin
plot_dat$p_Ra_nor = list(
  obs = x_Ra_new_obs$x_Ra_origin_obs[,o_nor,]/apply(x_Ra_new_obs$x_Ra_origin_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Ra_origin[year,1,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,o_nor,],
      lwr = array_format(tmp["2.5%",])[,o_nor,],
      upr = array_format(tmp["97.5%",])[,o_nor,]
    )
  }
)

# prep values to plot: carcass compositon age-3
plot_dat$p_Sa_prime_age3 = list(
  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_3,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,1,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,k_3,],
      lwr = array_format(tmp["2.5%",])[,k_3,],
      upr = array_format(tmp["97.5%",])[,k_3,]
    )
  }
)

# prep values to plot: carcass compositon age-4
plot_dat$p_Sa_prime_age4 = list(
  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_4,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,2,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,k_4,],
      lwr = array_format(tmp["2.5%",])[,k_4,],
      upr = array_format(tmp["97.5%",])[,k_4,]
    )
  }
)

# prep values to plot: weir compositon age-5
plot_dat$p_Sa_prime_age5 = list(
  obs = x_Sa_prime_new_obs$x_Sa_prime_age_obs[,k_5,]/apply(x_Sa_prime_new_obs$x_Sa_prime_age_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Sa_prime_age[year,3,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,k_5,],
      lwr = array_format(tmp["2.5%",])[,k_5,],
      upr = array_format(tmp["97.5%",])[,k_5,]
    )
  }
)

# prep values to plot: weir compositon origin
plot_dat$p_Sa_prime_nor = list(
  obs = x_Sa_prime_new_obs$x_Sa_prime_origin_obs[,o_nor,]/apply(x_Sa_prime_new_obs$x_Sa_prime_origin_obs, 3, rowSums),
  fitted = {
    tmp = post_summ(post, sub_index("^p_Sa_prime_origin[year,1,pop]", year = ".+", pop = ".+"))
    list(
      mn = array_format(tmp["mean",])[,o_nor,],
      lwr = array_format(tmp["2.5%",])[,o_nor,],
      upr = array_format(tmp["97.5%",])[,o_nor,]
    )
  }
)

# function to create plot for one data type
plot_f = function(dat_list, f, label = "", adj_label = FALSE) {

  with(dat_list, {

    # handle outlying values
    # obs[obs == 0] = NA
    # obs[obs == 1] = NA
    obs[obs == "NaN"] = NA

    # apply transformations
    obs = f(obs)
    mn = f(fitted$mn)
    lwr = f(fitted$lwr)
    upr = f(fitted$upr)

    # set fitted value to NA if no data value
    mn[is.na(obs)] = NA
    lwr[is.na(obs)] = NA
    upr[is.na(obs)] = NA

    # obtain axis limits
    lim = range(mn, lwr, upr, obs, na.rm = TRUE)

    # create the plot
    plot(mn ~ obs, xlim = lim, ylim = lim, pch = 21, col = solid_col, bg = tranp_col, cex = 1.5)

    # draw fitted value CRIs
    # segments(obs, lwr, obs, upr)

    # draw 1:1 line
    abline(0,1, lty = 2)

    # add text
    panel_label(label, x_inp = ifelse(adj_label, 0.05, 0.015), cex = 0.95)
  })
}

# identity function
ifun = function(x) x

# png("fig.png", h = 7 * ppi, w = 7.2 * ppi, res = ppi)
mypar(mfrow = c(1,1), oma = c(1.5,1.5,0,1.5), col.axis = "black", mar = c(1,0.75,0.5,0.25))
# r1 = rep(1:3, each = 4); r2 = rep(4:7, each = 3); r3 = rep(8:11, each = 3); r4 = rep(12:15, each = 3)
r1 = rep(1:3, each = 4); r2 = rep(4:9, each = 2); r3 = rep(10:13, each = 3); r4 = rep(14:17, each = 3)
layout(rbind(r1, r2, r3, r4))
# layout.show(17); dev.off()

# abundance plots
plot_f(plot_dat[["Pa_fall"]], ifun, "(a) Fall Trap Passage")
plot_f(plot_dat[["Mb_spring"]], ifun, "(b) Spring Trap Passage")
plot_f(plot_dat[["Ra_tot"]], ifun, "(c) Adult Return to River"); mtext(side = 4, text = "Abundance", outer = FALSE, line = 0.55)

# survival plots
plot_f(plot_dat[["phi_Pb_Ma"]], ifun, "(d) Summer \u2192 LGR", TRUE)
plot_f(plot_dat[["phi_Pa_Ma_fall"]], ifun, "(e) Fall \u2192 LGR", TRUE)
plot_f(plot_dat[["phi_Pa_Ma_winter"]], ifun, "(f) Winter \u2192 LGR", TRUE)
plot_f(plot_dat[["phi_Mb_Ma"]], ifun, "(g) Spring \u2192 LGR", TRUE)#; mtext(side = 4, text = "Survival", outer = FALSE, line = 0.75)
plot_f(plot_dat[["phi_Ma_O0"]], ifun, "(h) LGR \u2192 BON", TRUE)
plot_f(plot_dat[["phi_Rb_Ra"]], ifun, "(i) BON \u2192 LGR", TRUE); mtext(side = 4, text = "Survival", outer = FALSE, line = 0.55)

# composition plots
plot_f(plot_dat[["p_Ra_age3"]], ifun, "(j) Proportion Age-3")
plot_f(plot_dat[["p_Ra_age4"]], ifun, "(k) Proportion Age-4")
plot_f(plot_dat[["p_Ra_age5"]], ifun, "(l) Proportion Age-5")
plot_f(plot_dat[["p_Ra_nor"]], ifun, "(m) Proportion NOR"); mtext(side = 4, text = "Weir Composition", outer = FALSE, line = 0.55)

# composition plots
plot_f(plot_dat[["p_Sa_prime_age3"]], ifun, "(n) Proportion Age-3")
plot_f(plot_dat[["p_Sa_prime_age4"]], ifun, "(o) Proportion Age-4")
plot_f(plot_dat[["p_Sa_prime_age5"]], ifun, "(p) Proportion Age-5")
plot_f(plot_dat[["p_Sa_prime_nor"]], ifun, "(q) Proportion NOR"); mtext(side = 4, text = "Carcass Composition", outer = FALSE, line = 0.55)

# axis labels
axis_labels("Observed Value", "Fitted Value", yline = 0.25)

# dev.off(); file.show("fig.png")
```
